### 2016-07-28 presentations/coda2016/coda2016_poster.tex
jsm presentation

%%background from pptx
\usepackage{background}
\backgroundsetup{
scale=1,
angle=0,
opacity=1,  %% adjust
contents={\includegraphics[width=\paperwidth,height=\paperheight]{images/coda2016_poster_background.pdf}}
}

@@

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\input{images/rbm.tikz}}
  \caption{An example restricted Boltzmann machine (RBM), which consists of two layers, a hidden ($\mathcal{H}$) and a visible layer ($\mathcal{V}$), with no connections within a layer. Hidden nodes indicated by white circles and the visible nodes indicated by blue circles \cite{friedman2001elements}.}
  \label{fig:rbm}
\end{figure}

\vspace{1cm}
\begin{figure}[ht]
  \centering
  \input{images/visibles.tikz}
  \caption{Image classification using a RBM. On the left, each image pixel comprises a node in the visible layer, $\mathcal{V}$. On the right, the output of the RBM is used to create features which are then passed to a supervised learning algorithm.} 
  \label{fig:visibles}
\end{figure}

@@

%%-----------------------------------------------
%%
%%Top left box
%%
\begin{textblock}{14}(.65, 5.71)
{\large \bfseries Deep learning} \\[.25cm]
\begin{minipage}{.62\textwidth}
Three layer deep Boltzmann machine, with visible-to-hidden and hidden-to-hidden connections but no within-layer connections. This can be considered as multiple single layer restricted Boltzmann machines with the lower stack hidden layer acting as the visible layer for the higher stacked model. Claimed ability to learn "internal representations that become increasingly complex" \cite{salakhutdinov2009deep}, used in classification problems.
\end{minipage}
\begin{minipage}{.38\textwidth}
\begin{figure}
  \centering
  \input{images/deep_rbm.tikz}
  \caption{Deep RBM example.}
  \label{fig:deep_rbm}
\end{figure}
\end{minipage}

@@

For the $\{-1, 1 \}$ encoding of $\mathcal{V}$ and $\mathcal{H}$, the origin is the center of the parameter space. In particular, at $\boldsymbol \theta = \boldsymbol 0$, the RBM is equivalent to elements of $\boldsymbol X$ being distributed as iid Bernoulli$\left(\frac{1}{2}\right)$ $\Rightarrow$ No \emph{near-degeneracy}, \emph{instability}, or \emph{uninterpretability}!
\end{textblock}
\begin{textblock}{14.5}(.65, 23.9)
\begin{minipage}{.42\textwidth}
\begin{figure}[ht]
  \begin{minipage}{0.49\textwidth}
  \resizebox{\linewidth}{!}{
    \tdplotsetmaincoords{60}{-60}
    \input{images/toyhull_top.tikz}

    \draw(0,1,0) -- (1,0,0) -- (0,0,0) -- (0,1,0); 
     \draw(1,1,1) -- (1,0,0) -- (0,0,0) -- (1,1,1); 
     \draw(1,1,1) -- (0,1,0) -- (0,0,0) -- (1,1,1); 
     \draw(1,1,1) -- (0,1,0) -- (1,0,0) -- (1,1,1); 
    \end{tikzpicture}
  }
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
  \resizebox{\linewidth}{!}{
    \tdplotsetmaincoords{60}{-60}
    \input{images/toyhull_top_2.tikz}

    \draw(-1,1,-1) -- (1,-1,-1) -- (-1,-1,-1) -- (-1,1,-1); 
     \draw(1,1,1) -- (1,-1,-1) -- (-1,-1,-1) -- (1,1,1); 
     \draw(1,1,1) -- (-1,1,-1) -- (-1,-1,-1) -- (1,1,1); 
     \draw(1,1,1) -- (-1,1,-1) -- (1,-1,-1) -- (1,1,1); 
    \end{tikzpicture}
  }
  \end{minipage}
  \caption{The convex hulls of the statistic space in three dimensions for a toy RBM with $|\mathcal{V}| = |\mathcal{H}| = 1$ for $\{0,1\}$-encoding (left) and $\{-1,1\}$-encoding (right) enclosed by an unrestricted hull of 3-space.}
\label{fig:toyhull}
\end{figure}
\end{minipage}
\begin{minipage}{.02\textwidth}
\hfill
\end{minipage}
\begin{minipage}{.55\textwidth}
\begin{figure}
\centering
\includegraphics[scale=1]{images/frac_volume.pdf}
\label{fig:frac_volume}
\caption{Volume relationship for the convex hulls of statistics in $Q(\cdot)$ vs. unrestricted space.}
\end{figure}
\end{minipage}

@@

%%-----------------------------------------------
%%
%%Top right box
%%
\begin{textblock}{14}(32.4, 5.71)
{\large \bfseries Manageable (a.k.a. small) examples}
\begin{figure}
\centering
\includegraphics{images/degeneracy.pdf}
\includegraphics{images/instability.pdf}
\includegraphics{images/uninterpretability.pdf}
\label{fig:three_ways}
\caption{As the magnitude of $\boldsymbol \theta$ grows ($\boldsymbol \theta$ moves from $\boldsymbol 0$), so does the occurence of near-degeneracy, instability, and uninterpretability for RBMs of varying sizes.}
\end{figure}
\end{textblock}

@@

\begin{textblock}{14.54}(31.86, 25.5)
\begin{figure}
\centering
\includegraphics{images/image_prediction.pdf}
\label{fig:image_pred}
\vspace*{-15mm}
\caption{Posterior probability of each possible 4-pixel image using priors above.}
\end{figure}

>>>>

%%background from pptx
\usepackage{background}
\backgroundsetup{
scale=1,
angle=0,
opacity=1,  %% adjust
contents={\includegraphics[width=\paperwidth,height=\paperheight]{../images/coda2016_poster_background.pdf}}
}

@@

\begin{figure}[ht]
  \centering
  \resizebox{\linewidth}{!}{\input{../images/rbm.tikz}}
  \caption{An example restricted Boltzmann machine (RBM), which consists of two layers, a hidden ($\mathcal{H}$) and a visible layer ($\mathcal{V}$), with no connections within a layer. Hidden nodes indicated by white circles and the visible nodes indicated by blue circles \cite{friedman2001elements}.}
  \label{fig:rbm}
\end{figure}

\vspace{1cm}
\begin{figure}[ht]
  \centering
  \input{../images/visibles.tikz}
  \caption{Image classification using a RBM. On the left, each image pixel comprises a node in the visible layer, $\mathcal{V}$. On the right, the output of the RBM is used to create features which are then passed to a supervised learning algorithm.} 
  \label{fig:visibles}
\end{figure}

@@

%%-----------------------------------------------
%%
%%Top left box
%%
\begin{textblock}{14}(.65, 5.71)
{\large \bfseries Deep learning} \\[.25cm]
\begin{minipage}{.62\textwidth}
Three layer deep Boltzmann machine, with visible-to-hidden and hidden-to-hidden connections but no within-layer connections. This can be considered as multiple single layer restricted Boltzmann machines with the lower stack hidden layer acting as the visible layer for the higher stacked model. Claimed ability to learn "internal representations that become increasingly complex" \cite{salakhutdinov2009deep}, used in classification problems.
\end{minipage}
\begin{minipage}{.38\textwidth}
\begin{figure}
  \centering
  \input{../images/deep_rbm.tikz}
  \caption{Deep RBM example.}
  \label{fig:deep_rbm}
\end{figure}
\end{minipage}

@@

For the $\{-1, 1 \}$ encoding of $\mathcal{V}$ and $\mathcal{H}$, the origin is the center of the parameter space. In particular, at $\boldsymbol \theta = \boldsymbol 0$, the RBM is equivalent to elements of $\boldsymbol X$ being distributed as iid Bernoulli$\left(\frac{1}{2}\right)$ $\Rightarrow$ No \emph{near-degeneracy}, \emph{instability}, or \emph{uninterpretability}!
\end{textblock}
\begin{textblock}{14.5}(.65, 23.9)
\begin{minipage}{.42\textwidth}
\begin{figure}[ht]
  \begin{minipage}{0.49\textwidth}
  \resizebox{\linewidth}{!}{
    \tdplotsetmaincoords{60}{-60}
    \input{../images/toyhull_top.tikz}

    \draw(0,1,0) -- (1,0,0) -- (0,0,0) -- (0,1,0); 
     \draw(1,1,1) -- (1,0,0) -- (0,0,0) -- (1,1,1); 
     \draw(1,1,1) -- (0,1,0) -- (0,0,0) -- (1,1,1); 
     \draw(1,1,1) -- (0,1,0) -- (1,0,0) -- (1,1,1); 
    \end{tikzpicture}
  }
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
  \resizebox{\linewidth}{!}{
    \tdplotsetmaincoords{60}{-60}
    \input{../images/toyhull_top_2.tikz}

    \draw(-1,1,-1) -- (1,-1,-1) -- (-1,-1,-1) -- (-1,1,-1); 
     \draw(1,1,1) -- (1,-1,-1) -- (-1,-1,-1) -- (1,1,1); 
     \draw(1,1,1) -- (-1,1,-1) -- (-1,-1,-1) -- (1,1,1); 
     \draw(1,1,1) -- (-1,1,-1) -- (1,-1,-1) -- (1,1,1); 
    \end{tikzpicture}
  }
  \end{minipage}
  \caption{The convex hulls of the statistic space in three dimensions for a toy RBM with $|\mathcal{V}| = |\mathcal{H}| = 1$ for $\{0,1\}$-encoding (left) and $\{-1,1\}$-encoding (right) enclosed by an unrestricted hull of 3-space.}
\label{fig:toyhull}
\end{figure}
\end{minipage}
\begin{minipage}{.02\textwidth}
\hfill
\end{minipage}
\begin{minipage}{.55\textwidth}
\begin{figure}
\centering
\includegraphics[scale=1]{../images/frac_volume.pdf}
\label{fig:frac_volume}
\caption{Volume relationship for the convex hulls of statistics in $Q(\cdot)$ vs. unrestricted space.}
\end{figure}
\end{minipage}

@@

%%-----------------------------------------------
%%
%%Top right box
%%
\begin{textblock}{14}(32.4, 5.71)
{\large \bfseries Manageable (a.k.a. small) examples}
\begin{figure}
\centering
\includegraphics{../images/degeneracy.pdf}
\includegraphics{../images/instability.pdf}
\includegraphics{../images/uninterpretability.pdf}
\label{fig:three_ways}
\caption{As the magnitude of $\boldsymbol \theta$ grows ($\boldsymbol \theta$ moves from $\boldsymbol 0$), so does the occurence of near-degeneracy, instability, and uninterpretability for RBMs of varying sizes.}
\end{figure}
\end{textblock}

@@

\begin{textblock}{14.54}(31.86, 25.5)
\begin{figure}
\centering
\includegraphics{../images/image_prediction.pdf}
\label{fig:image_pred}
\vspace*{-15mm}
\caption{Posterior probability of each possible 4-pixel image using priors above.}
\end{figure}
